SDC: Social Dispersed Computing

### 2017-06-23 papers/IARPA-RFI-17-03/rfi.tex
update

Transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (i.e., those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodians of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}.

\Aron{I am not sure what this sentence was supposed to say.}
These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.  With social dispersed computing, energy consumers, producers, and storage solutions in a transactive grid will be discovered automatically and monitored continuously, and system status will be updated in case devices appear to be offline.

@@

However, the computing structure in these systems does not focus on the privacy challenges that arise from the
required information exchange in this decentralized transactive
system: 
\begin{itemize}
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers:} 
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. %In comparison, secure
%  smart metering reveals the prosumers' energy usage patterns only to
%  the operator.

@@

Since urban spaces are expanding at impressive rates, an efficient transportation system is a key component to any well-functioning city. Yet, as cities expand, existing infrastructures are stressed to their limits. To make the problem worse,  building new infrastructures is expensive, time consuming, and disruptive. Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transportation operated by both cities and private users. However, given the large number of choices and available options, this often leads to a \Aron{Does this alway boil down to a dynamic programming problem in the algorithmic sense?} dynamic programming problem that must be solved online, considering several state variables, such as traffic congestion, mode capacity, and personal preferences.

@@

\subsubsection{Privacy Problem}
A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities. This platform must offer mixed-mode routing suggestions and general system information to travelers and---in turn---supply service providers with high-fidelity information about how users are consuming different transportation resources. At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale. Alternatively, a novel proof-of-concept that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.

>>>>

Transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (i.e., those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodians of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}.
%\Aron{I am not sure what this sentence was supposed to say.}
%These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
%\cite{gunthersmart}, and the Resilient Information Architecture
%Platform for Smart Grid (RIAPS)
%\cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.  
With social dispersed computing, energy consumers, producers, and storage solutions in a transactive grid will be discovered automatically and monitored continuously, and system status will be updated in case devices appear to be offline.

@@

The computing structure in these systems does not focus on the privacy challenges that arise from the
required information exchange:
\begin{itemize}
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers:} 
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. %In comparison, secure
%  smart metering reveals the prosumers' energy usage patterns only to
%  the operator.

@@

Since urban spaces are expanding at impressive rates, an efficient transportation system is a key component to any well-functioning city. Yet, as cities expand, existing infrastructures are stressed to their limits. To make the problem worse,  building new infrastructures is expensive, time consuming, and disruptive. Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transportation operated by both cities and private users. However, given the large number of choices and available options, this can lead to a %\Aron{Does this alway boil down to a dynamic programming problem in the algorithmic sense?} 
dynamic programming problem that must be solved online, considering several state variables, such as traffic congestion, mode capacity, and personal preferences.

@@

\subsubsection{Privacy Problem}
A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities. This platform must offer mixed-mode routing suggestions and general system information to travelers and---in turn---supply service providers with high-fidelity information about how users are consuming different transportation resources. At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale. Alternatively, a social dispersed computing approach that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.
